SOL Filamentary transport: update from joint AUG-TCV MST1 experiment

### 2018-01-24 Meetings/25ITPADivSOL/vianello_25itpadivsol.tex

\documentclass[10pt, compress]{beamer}
\usetheme[conference=25th ITPA-DivSOL,venue=Chengdu, date=29/01/2018, titleprogressbar, logo=RFX-logo]{Eurof}
\usepackage{listings,amsmath,multimedia, amssymb}
\usepackage{tangocolors}
\usepackage{rfxcolor}
% multiple figure location
%\graphicspath{{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/}{../Experiments/}}
% for drawing
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,shapes,backgrounds}
\usepackage{onimage}
\usepackage[export]{adjustbox}
% for font
\usepackage[absolute,overlay]{textpos}
  \setlength{\TPHorizModule}{1mm}
  \setlength{\TPVertModule}{1mm}

\usepackage[style=nature,citestyle=authoryear-comp,defernumbers=true,maxnames=2,firstinits=true,
uniquename=init,backend=bibtex8,arxiv=abs,mcite]{biblatex}
\bibliography{biblio}
\renewcommand*{\bibfont}{\footnotesize}
\renewcommand*{\citesetup}{\footnotesize}
\usepackage[export]{adjustbox}
\makeatother
\mode<presentation>
\makeatletter
% add a macro that saves its argument
\newcommand{\footlineextra}[1]{\gdef\insertfootlineextra{#1}}
\newbox\footlineextrabox
% for reducing font on a single slide
\newcommand\Fontvi{\fontsize{8}{7.2}\selectfont}
\title{SOL Filamentary transport: update from joint AUG-TCV MST1 experiment}
\date{29 January 2018}
\author[N.Vianello]{presented by N. Vianello}
\begin{document}
\tikzstyle{every picture}+=[remember picture]
\maketitle
\begin{frame}{Scientific team}
  \centering{
  Volker Naulin, Jiri Adamek, Matteo Agostini, Diogo Aguiam, Scott Allan, Matthias Bernert, Daniel Carralero Ortiz, 
Stefan Costea, Istvan Cziegler, Hugo De Oliveira, Joaquin Galdon-Quiroga, Gustavo Grenfell, Antti Hakola, 
Codrina Ionita-Schrittwieser, Heinz Isliker, Alexander Karpushov, Jernej Kovacic, Benoît Labit, Florian Laggner, Jens Madsen, 
Roberto Maurizio, Ken McClements, Fulvio Militello, Jeppe Miki Busk Olsen, Jens Juul Rasmussen, Timo Ravensbergen, Bernd Sebastian Schneider, Roman Schrittwieser, Jakub Seidl, Monica Spolaore, Christian Theiler, Cedric Kar-Wai Tsui, Kevin Verhaegh, Jose Vicente, 
Nickolas Walkden, Zhang Wei, Elisabeth Wolfrum, W. Vijvers}
j\end{frame}

@@

\begin{frame}{Current scan at constant q$_{95}$}
  \begin{columns}
    \begin{column}{0.6\textwidth}
      \includegraphics<1>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EquilibriaIpScanConstantQ95}
      \includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantq95}
      \includegraphics<3>[width=.9\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantQ95}
      \includegraphics<4>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/NeutralsVsGreenwaldConstantQ95}
      \includegraphics<5>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/UpstreamTargetProfilesConstantQ95}
      \includegraphics<6>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CompareTargetProfilesConstantQ95}
      \includegraphics<7>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/AmplitudeVsLambdaIpConstantQ95}
      \includegraphics<8>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EfoldVBlobAllColorConstantQ95}         
      \includegraphics<9>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/BlobLambdaAllColorConstantQ95}         
    \end{column}
    \begin{column}{0.4\textwidth}
      \begin{itemize}
        \item<1|only@1> Shape matched in within the single scan even
          though this required for TCV operation with very low
          toroidal field (0.8T)
        \item<1|only@1> The parallel connection length remains almost unchanged
        \item<2|only@2> AUG: As for the case of constant B$_t$ we have
          pretty reproducible behavior matching basically the plasma
          condition in within the current scan
        \item<3|only@3> TCV: Even at such an high density at lower
          current (and lower B$_t$) no sign of target ion flux
          rollover/detachment
        \item<4|only@4> AUG: Divertor neutral density exhibits still
          the same behavior is considered as a function of greenwald fraction
        \item<5|only@5> For AUG upstream and target profiles exhibit
          the same behavior with flattening observed at large values
          of $\Lambda_{div}$. TCV actually even at high value of
          density no sign of upstream profile flattening \alert{even
            at very large values of $\Lambda_{div}$}
        \item<6|only@6> This is due to the fact we did not reach
          divertor detachment which \alert{seems necessary for
            upstream profile modification}  
        \item<7|only@7> AUG: Amplitude evolution as a function of $\Lambda_{div}$ 
          still reconcile the explored current scan
        \item<8|only@8> AUG exhibit consistently an increase of
          $\lambda_n$ with blob-size whereas for TCV the profile
          remains flat consistently with a small variation of
          $\delta_b$
        \item<9|only@9> And for TCV this is true even at high value of $\Lambda_{div}$

      \end{itemize}
    \end{column}
  \end{columns}

@@

>>>>

\documentclass[10pt, compress]{beamer}
\usetheme[conference=25th ITPA-DivSOL,venue=Chengdu, date=29/01/2018, titleprogressbar, logo=RFX-logo]{Eurof}
\usepackage{listings,amsmath,multimedia, amssymb}
\usepackage{tangocolors}
\usepackage{rfxcolor}
\definecolor{colorA}{HTML}{324D5C}
\definecolor{colorB}{HTML}{E37B40}
\definecolor{colorC}{HTML}{60A65F}
% multiple figure location
%\graphicspath{{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/}{../Experiments/}}
% for drawing
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,shapes,backgrounds}
\usepackage{onimage}
\usepackage[export]{adjustbox}
% for font
\usepackage[absolute,overlay]{textpos}
  \setlength{\TPHorizModule}{1mm}
  \setlength{\TPVertModule}{1mm}

\usepackage[style=nature,citestyle=authoryear-comp,defernumbers=true,maxnames=2,firstinits=true,
uniquename=init,backend=bibtex8,arxiv=abs,mcite]{biblatex}
\bibliography{biblio}
\renewcommand*{\bibfont}{\footnotesize}
\renewcommand*{\citesetup}{\footnotesize}
\usepackage[export]{adjustbox}
\makeatother
\mode<presentation>
\makeatletter
% add a macro that saves its argument
\newcommand{\footlineextra}[1]{\gdef\insertfootlineextra{#1}}
\newbox\footlineextrabox
% for reducing font on a single slide
\newcommand\Fontvi{\fontsize{8}{7.2}\selectfont}
\title{SOL Filamentary transport: update from joint AUG-TCV MST1 experiment}
\date{29 January 2018}
\author[N.Vianello]{presented by N. Vianello for the MST1-Topic 21
  scientific team}
\begin{document}
\tikzstyle{every picture}+=[remember picture]
\maketitle
\begin{frame}{Scientific team}
  \centering{
  Volker Naulin, Jiri Adamek, Matteo Agostini, Diogo Aguiam, Scott Allan, Matthias Bernert, Daniel Carralero Ortiz, 
Stefan Costea, Istvan Cziegler, Hugo De Oliveira, Joaquin Galdon-Quiroga, Gustavo Grenfell, Antti Hakola, 
Codrina Ionita-Schrittwieser, Heinz Isliker, Alexander Karpushov, Jernej Kovacic, Benoît Labit, Florian Laggner, Jens Madsen, 
Roberto Maurizio, Ken McClements, Fulvio Militello, Jeppe Miki Busk Olsen, Jens Juul Rasmussen, Timo Ravensbergen, Bernd Sebastian Schneider, Roman Schrittwieser, Jakub Seidl, Monica Spolaore, Christian Theiler, Cedric Kar-Wai Tsui, Kevin Verhaegh, Jose Vicente, 
Nickolas Walkden, Zhang Wei, Elisabeth Wolfrum, W. Vijvers}
j\end{frame}

@@

\begin{frame}{Current scan at constant q$_{95}$}
  \begin{columns}
    \begin{column}{0.6\textwidth}
      \includegraphics<1>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EquilibriaIpScanConstantQ95}
      \includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantq95}
      \includegraphics<3>[width=.9\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantQ95}
      \includegraphics<4>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/NeutralsVsGreenwaldConstantQ95}
      \includegraphics<5>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/UpstreamTargetProfilesConstantQ95}
      \includegraphics<6>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CompareTargetProfilesConstantQ95}
      \includegraphics<7>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/AmplitudeVsLambdaIpConstantQ95}
      \includegraphics<8>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EfoldVBlobAllColorConstantQ95}         
      \includegraphics<9>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/BlobLambdaAllColorConstantQ95}         
    \end{column}
    \begin{column}{0.4\textwidth}
      \begin{itemize}
        \item<1|only@1> Shape matched in within the single scan even
          though this required for TCV operation with very low
          toroidal field (0.8T)
        \item<1|only@1> The parallel connection length remains almost unchanged
        \item<2|only@2> AUG: As for the case of constant B$_t$ we have
          pretty reproducible behavior matching basically the plasma
          condition in within the current scan
        \item<3|only@3> TCV: Even at such an high density at lower
          current (and lower B$_t$) no sign of target ion flux
          rollover/detachment
        \item<4|only@4> AUG: Divertor neutral density exhibits still
          the same behavior is considered as a function of greenwald fraction
        \item<5|only@5> For AUG upstream and target profiles exhibit
          the same behavior with flattening observed at large values
          of $\Lambda_{div}$. TCV actually even at high value of
          density no sign of upstream profile flattening \alert{even
            at very large values of $\Lambda_{div}$}
        \item<6|only@6> This is due to the fact we did not reach
          divertor detachment which \alert{seems necessary for
            upstream profile modification}  
        \item<7|only@7> AUG: Amplitude evolution as a function of $\Lambda_{div}$ 
          still reconcile the explored current scan
        \item<8|only@8> AUG exhibit consistently an increase of
          $\lambda_n$ with blob-size whereas for TCV the profile
          remains flat consistently with a small variation of
          $\delta_b$
        \item<9|only@9> And for TCV this is true even at high value of $\Lambda_{div}$
      \end{itemize}
    \end{column}
  \end{columns}

@@

%% H-Mode same fueling
\begin{frame}{H-Mode analysis on AUG}
    \Fontvi
  \vspace{-1cm}
  \begin{columns}
  \begin{column}{0.55\textwidth}
    \centering{\includegraphics<1>[height=0.8\textheight]{../../Experiments/AUG/analysis/pdfbox/GeneralComparisonShot34276_34278_34281.pdf}}
    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/PuffingIpolsola34276_34278_34281}}
  \centering{\includegraphics<4>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EfoldSizeShots34276_34278}}
  \centering{\includegraphics<5>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EfoldSizeShots34276_34278_34281}}
  \end{column}
  \begin{column}{0.45\textwidth}
    \begin{itemize}
    \item<1|only@1> We perform a series of shots in H-Mode with 6.5
      total heating power where we changed the fueling and the
      efficiency of cryopumps. Specifically we have
      \begin{itemize}
        \item<1|only@1>\textcolor{colorA}{\# 34276 without the
            cryompumps}
        \item<1|only@1> \textcolor{colorB}{\# 34278 with the same
            fueling as \# 34276 but with the cryompump}
        \item<1|only@1> \textcolor{colorC}{\#34281 where we increase
            fueling and seeding trying to mimic the same subdivertor
            pressure as \# 34276}
      \end{itemize}
    \item<1|only@1> Keeping the same fueling with the cryopump clearly
      reduce the pressure in the the sub-divertor area, we don't reach
      clear detachment and the edge density is constant even during
      the fueling ramp. Degraded H-mode reached later without the cryopump

    \item<2|only@2> Different behavior of ELM during the fueling
      ramp. ELM size and frequency changes strongly without the
      cryopump or during extreme fueling case
    \item<3|only@3> Profiles
    \item<4|only@4> Without the cryopumps, we reached flatter
         profiles with comparable inter-ELM resolved blob-size. This
         indicates strong neutral pressure effects in determining
         upstream profiles
    \item<5|only@5> Increasing the fueling and correspondingly the
      divertor neutral pressure move towards a situation similar to
      \# 34276 without the cryopump
      \end{itemize}
  \end{column}
\end{columns}
\end{frame}

\begin{frame}{Conclusion}
  \Fontvi
  \begin{itemize}
    \item Current scan at constant B$_t$ and at constant q$_{95}$
      performed during density ramps L-Mode experiments both at AUG
      and TCV
    \item In both the case shoulder appear earlier in density at lower
      current but AUG shows reconciliation of behavior if considered
      as a function of greenwald fraction and $\Lambda_{div}$
    \item Both the experiments exhibit at constant B$_t$ flattening of the profile as
      blob size is increasing, independently from the current. The
      same behavior is observed during current scan at constant
      q$_{95}$ \alert{only on AUG}
    \item On TCV during the current scan at constant q$_{95}$
      detachment not reached and this \alert{prevent upstream profile
        flattening}
    \item H-Mode experiments performed on AUG where fueling and
      pumping have been varied. Proved inter-ELM profile flattening
      also in H-Mode with a more efficient puffing without the
      cryopump. \alert{Hints on the role of neutrals also in H-Mode}
  \end{itemize}
\end{frame}

\begin{frame}{D$_{\alpha}$ tomography: work in progress}
\Fontvi
  \begin{columns}
    \begin{column}{0.5\textwidth}
      \includegraphics<1>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/Dalpha/inv_alfa_34104_2000}
      \includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/Dalpha/inv_alfa_34104_2700}
      \includegraphics<3>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/Dalpha/inv_alfa_34104_3100}
    \end{column}
    \begin{column}{0.5\textwidth}
      \begin{itemize}
        \item \alert{Preliminary} results from inversion tomography
          from calibrated D$_{\alpha}$ camera under the assumption of
          toroidally symmetric emission limited to the region outside
          the LCFS
        \item \emph{Simultaneous Algebraic Reconstruction Technique
            (SART) (A.H. Anderson and A.C.Kak,  Ultrasonic Imaging
            \textbf{6},  81 (1984))}
        \item As time evolves during the L-Mode ramp we observe
          D$_{\alpha}$ radiation moving from HFS towards the LFS
          common flux region
        \item \alert{This is consistent with JET observation in
            Horizontal target regime whenever shoulder is observed}
      \end{itemize}
    \end{column}
  \end{columns}
\end{frame}
